%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
{\Huge \scshape KARTHIKEYAN S} \\[1pt]
\small
\faPhone\ +91~7708580054 \quad
\faEnvelope\ karthikeyanselvam260906@gmail.com \quad
\faLinkedin\ \href{https://www.linkedin.com/in/karthikeyan-s-657338291}{karthikeyan-s} \quad
\faGithub\ \href{https://github.com/karthikeyan261222}{karthikeyan261222}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chennai Institute of Technology}{Sep 2023 -- May 2027}
      {Bachelor of Engineering in Computer Science Engineering (AI–ML) \textbf{— CGPA: 8.88}}{Chennai, Tamil Nadu}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {HCL Technologies}{November 2024 -- February 2025}
    {AI Intern}{Sholinganallur, Chennai (Onsite)}
    \resumeItemListStart
      \resumeItem{Worked on \textbf{Godseye}, a unified AI framework with five custom architectures for training, inference, data augmentation, camera input, and logging.}
      \resumeItem{Improved model accuracy by \textbf{20\%} compared to YOLO11 through architectural optimization and experimentation.}
      \resumeItem{Built an AI research assistant for intelligent knowledge extraction, semantic search, and structured note organization using Large Language Models (LLMs).}
      \resumeItem{Hands-on experience with Agentic AI tools including Autogen, Promptflow, Langflow, LangChain, MCP, and CrewAI.}
    \resumeItemListEnd

  \resumeSubheading
    {Kanini Software Solutions}{May 2024 -- June 2024}
    {Data Analyst Intern}{Chennai (Onsite)}
    \resumeItemListStart
      \resumeItem{Developed a healthcare call center analytics system using the Whisper model for audio transcription and segmentation.}
      \resumeItem{Ensured HIPAA compliance while handling sensitive healthcare conversations for quality assurance.}
      \resumeItem{Performed sentiment analysis to assess call quality and agent performance.}
      \resumeItem{Created analytical dashboards using Tableau, Power BI, and Python libraries.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart


\resumeProjectHeading
    {\textbf{AWS CI/CD Pipeline for Containerized Application} $|$ \emph{AWS CodePipeline, CodeBuild, CodeDeploy, Docker, Flask, EC2}}{}
\resumeItemListStart
      \resumeItem{Built and deployed an end-to-end CI/CD pipeline on AWS to automate build, test, and deployment of a containerized Flask application to EC2.}
      \resumeItem{Automated Docker image build and push workflows, integrating AWS Parameter Store for secure credential and secrets management.}
      \resumeItem{Configured automated deployment lifecycle hooks for reliable zero-touch container rollout, eliminating manual deployment steps.}
\resumeItemListEnd
    \vspace{-17pt}

\resumeProjectHeading
{\textbf{DevSecOps CI/CD Pipeline} $|$ \emph{GitHub, Jenkins, SonarQube, Docker, Kubernetes (AWS EKS), ArgoCD}}{}
\resumeItemListStart
\resumeItem{Built an automated CI/CD pipeline using Jenkins, SonarQube, Docker, and Kubernetes, integrating GitOps deployment via ArgoCD on AWS EKS.}
\resumeItem{Enforced code quality gates with SonarQube static analysis before builds proceed to deployment.}
\resumeItem{Integrated security scanning and monitoring using Trivy, Prometheus, and Grafana, reducing manual intervention across the pipeline.}
\resumeItemListEnd
\vspace{-17pt}
\resumeProjectHeading
    {\textbf{Terraform EKS Infrastructure Automation} $|$ \emph{Terraform, AWS EKS, VPC, Kubernetes, IAM}}{}
    \resumeItemListStart
      \resumeItem{Provisioned a production-style Amazon EKS cluster and multi-AZ VPC using Terraform, fully automating networking, security groups, and node groups as Infrastructure as Code.}
      \resumeItem{Configured IRSA (IAM Roles for Service Accounts) to enforce least-privilege, pod-level AWS permissions instead of broad node-level IAM roles.}
      \resumeItem{Designed auto-scaling worker node groups and public/private subnet architecture with proper Kubernetes load balancer subnet tagging.}
    \resumeItemListEnd
    \vspace{-16pt}




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\small{

\textbf{Agentic AI \& LLM Tools:} Autogen, Promptflow, Langflow, LangChain, CrewAI, MCP \\
\textbf{Analytics \& Visualization:} Tableau, Power BI, Python Libraries \\
\textbf{Programming Languages:} Python and Java\\
\textbf{DevOps \& Cloud:} Git/GitHub, Linux, AWS, Jenkins, Docker, Terraform, Ansible, Prometheus, Grafana \\

}
\vspace{-10pt}

%------RELEVANT COURSEWORK-------
\section{Certifications}
    %\resumeSubHeadingListStart
        \begin{multicols}{3}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small AWS Solutions Architect(SAA-C03)
                \item AWS Cloud Practitioner(CLF-C02)
                \item Data Analysis and Visualisation
                \item Data Analysis with Python
                \item IBM - Cloud computing
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd
%-----------INVOLVEMENT---------------
\section{Achievements \& Hackathons}
\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, itemsep=2pt, topsep=0pt]
\small{
    \item \textbf{2× AWS Certified – SAA-C03 and CLF-C02 Certified Professional}
    
    \item \textbf{Intel OneAPI Hackathon – Finalist}
}
\end{itemize}
\vspace{-19pt}



\end{document}
